Modeling potential JCPOA diversion scenarios using Cyclus

### 2018-01-27 paper.tex
human readable assay :)

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modeling potential JCPOA breakout scenarios using Cyclus}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.7]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src correspond to an
      infinite source of natural uranium, cascade\_ $n$ and storage\_ $n$
      corresponds respectively to the cascades, and the storage getting the
  products of the cascades at the level $n$.}\label{fig:flow}
\end{figure}

@@

The case 1 is designed to configure 30 cascades in the scenario (the maximum
allowable under the JCPOA agreement), all designed the same way. The basic
properties are: less than 169 centrifuges per cascade, F/P/T assays of
0.0071/0.035/0.003. The corresponding design includes 167 centrifuges, with
respective F/P/T assays of 0.0071/0.0412842/0.00290548.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in
Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
to produce an uranium product enrich at $98\%$ while the second case is only
able to reach an enrichment of $88.3\%$ with the same number of levels.

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modeling potential JCPOA diversion scenarios using Cyclus}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src corresponds to an
  infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_ $\{n\}$
      corresponds to the cascade and the storage getting the
      products of the cascades at the level $\{n\}$.}\label{fig:flow}
\end{figure}

@@

The case 1 is designed to configure 30 cascades in the scenario (the maximum
allowable under the JCPOA agreement), all designed the same way. The basic
properties are: less than 169 centrifuges per cascade, F/P/T assays of
0.0071/0.035/0.003. The corresponding design includes 167 centrifuges, with
respective F/P/T assays of 0.0071/0.0413/0.0029.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in
Figure \ref{fig:assay_c1_nr} and \ref{fig:assay_c2_nr}, the first case is able
to produce an uranium product enrich at $98\%$ while the second case is only
able to reach an enrichment of $88.3\%$ with the same number of levels.
